Technical Report

### 2017-10-26 fully-abstract-comp/technical-report.tex
updated value relation
added some stuff on the worlds

\newcommand{\World}{\mathrm{World}}

@@

\section{Logical Relation}
\lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
\lau{19-10-2017: Maybe linearity should be taken care of in just one place (instead of in $\lrr$ relation and mem staisfaction). That is, add a predicate that checks whether the configuration satisfies linearity (such a condition may be to syntactic to work?).}
In the following definitions, \src{blue} is used to indicate values related to the source machine. This is unlike previous definitions, where \src{blue} is used  indicate source language specific parts of definitions.
\[
  \lre(W) = \left\{ \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{k_{d,S}}, \src{k_{c,S}}, k_{d,T}, k_{c,T}, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrk, W_\lrr, W_\lrm \ldotp \\
      \qquad\npair[n']{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair[.]{k_{d,S},k_{c,S}}{k_{d,T},k_{c,T}}} \in \lrk(W_\lrk) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrr) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Rightarrow\\
      \qquad\npair[n']{\left(\array{l}\src{(\ms_S,\reg_S\updReg{\pcreg,\rdata,\rretc,\rretd}{v_{c,S},v_{d,S},k_{c,S},k_{d,S}},\stk, \ms_\stk)},\\
                                          (\ms_T,\reg_T\updReg{\pcreg,\rdata,\rretc,\rretd}{v_{c,T},v_{d
,T},k_{c,T},k_{d,T}})\endarray\right)}
      \in \lro(W\uplus W_\lrk \uplus W_\lrr \uplus W_\lrm)
    \end{array}
    \right\}
\]
\lau{24-10-2017: Dominique, I do not see how the splitting of worlds is going to work out. I can see how it will enforce linearity, but is you give a "pure" region (the kind of region that is only allowed to go to one part of a split) to the $\lrr$-relation, then the memory satisfation does not have it, and it cannot find a memory segment for this part. In other words, the memory satisfaction will not be able to find a concrete memory segment for segments governed by a linear capability in the register file. Maybe the memory satisfaction should have all of the parts, so it can represent them (but also limit what linear capabilities can be used).}

@@

\[
  \lrv(W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \middle| i \in \ints \right\}\cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrc(\sigma,\_)},\\\sealed{\sigma,\vsc_C}\endarray\right)} \middle| 
    \begin{array}{l}
    \forall n'<n, W' \pubft W, \npair[n']{\stpair[.]{\retptrd(\sigma,\_)}{\sealed{\sigma,\vsc_D}}} \in \lrv(W') \ldotp\\
      \npair[n']{\retptrc(\sigma,\_),\retptrd(\sigma,\_),\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W')
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrd(\sigma,\_)},\\\sealed{\sigma,\vsc_D}\endarray\right)} \middle| 
    \begin{array}{l}
    \forall n'<n, W' \pubft W, \npair[n']{\stpair[.]{\retptrc(\sigma,\_)}{\sealed{\sigma,\vsc_C}}} \in \lrv(W') \ldotp\\
      \npair[n']{\src{\retptrc(\sigma,\_)},\src{\retptrd(\sigma,\_)},\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W')
    \end{array}
    \right\}\cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \middle| \right)}
    \right\}
  \end{array}
\]

>>>>

\newcommand{\World}{\mathrm{World}}
\newcommand{\RegionName}{\mathrm{RegionName}}
\newcommand{\Region}{\mathrm{Region}}
\newcommand{\pureReg}{\mathrm{pure}}
\newcommand{\normalReg}{\mathrm{normal}}
\newcommand{\State}{\mathrm{State}}
\newcommand{\Rels}{\mathrm{Rels}}
\newcommand{\UPred}[1]{\mathrm(#1)}

@@

\section{Logical Relation}
\subsection{Worlds}
\[
  \World = \RegionName \parfun 2 \times \Region
\]
where $\RegionName = \nats$
\[
  \Region = \left\{
  \begin{array}{l}
    \{\pureReg \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
    \{\normalReg \} \times \State \times \Rels \times (\State \fun \World \fun \UPred{\MemSeg^2})\\
  \end{array} \right.
\]
\lau{26-20-2017: It is not clear to me what the monotonicity requirements on the memory interpretation functions should be.}
\[
  W_1 \uplus W_1 = W
  \begin{array}[t]{l}
    \text{if $\dom(W) = \dom(W_1) = \dom(W_2) \tand$} \\
    \forall r \in \dom(W) \ldotp W(r) = W_1(r) \oplus W_2(r)
  \end{array}
\]
$\oplus$ is defined as follows
\begin{align*}
  (i,\normalReg,\var{sm}) \uplus (j,\normalReg,\var{sm}) = & (\max(i,j),\normalReg,\var{sm}) \\
  (1,\pureReg,\var{sm}) \uplus (0,\pureReg,\var{sm}) = & (1,\pureReg,\var{sm}) \\
  (0,\pureReg,\var{sm}) \uplus (1,\pureReg,\var{sm}) = & (1,\pureReg,\var{sm}) \\
  (0,\pureReg,\var{sm}) \uplus (0,\pureReg,\var{sm}) = & (0,\pureReg,\var{sm}) \\
\end{align*}
and for all other cases $\oplus$ is undefined. Specifically, $\uplus$ is not defined when both sides are an owned $\pureReg$-region. It is further not defined if the two sides do not agree on region type and state machine.

\subsection{Relation}
\lau{19-10-2017: Rest of source configuration needs to come from somewhere in $\lre$.}
\lau{19-10-2017: Maybe linearity should be taken care of in just one place (instead of in $\lrr$ relation and mem staisfaction). That is, add a predicate that checks whether the configuration satisfies linearity (such a condition may be to syntactic to work?).}
In the following definitions, \src{blue} is used to indicate values related to the source machine. This is unlike previous definitions, where \src{blue} is used  indicate source language specific parts of definitions.
\[
  \lre(W) = \left\{ \npair{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \middle| 
    \begin{array}{l}
      \forall n' \leq n, \src{k_{d,S}}, \src{k_{c,S}}, k_{d,T}, k_{c,T}, \src{\reg_S}, \reg_T, \src{\ms_S}, \ms_T, \src{\ms_\stk}, \src{\stk} \ldotp\\
      \quad \forall W_\lrk, W_\lrr, W_\lrm \ldotp \\
      \qquad\npair[n']{\stpair[.]{v_{c,S},v_{d,S}}{v_{c,T},v_{d,T}}} \in \lrp(W) \wedge \\
      \qquad\npair[n']{\stpair[.]{k_{d,S},k_{c,S}}{k_{d,T},k_{c,T}}} \in \lrk(W_\lrk) \wedge \\
      \qquad\npair[n']{\stpair{\reg}{\reg}} \in \lrr(W_\lrr) \wedge\\
      \qquad\memSat[n']{\stpair[.]{\ms_S,\stk,\ms_\stk}{\ms_T}}{W_\lrm} \\
      \qquad\Rightarrow\\
      \qquad\npair[n']{\left(\array{l}\src{(\ms_S,\reg_S\updReg{\pcreg,\rdata,\rretc,\rretd}{v_{c,S},v_{d,S},k_{c,S},k_{d,S}},\stk, \ms_\stk)},\\
                                          (\ms_T,\reg_T\updReg{\pcreg,\rdata,\rretc,\rretd}{v_{c,T},v_{d
,T},k_{c,T},k_{d,T}})\endarray\right)}
      \in \lro(W\uplus W_\lrk \uplus W_\lrr \uplus W_\lrm)
    \end{array}
    \right\}
\]
\lau{24-10-2017: Dominique, I do not see how the splitting of worlds is going to work out. I can see how it will enforce linearity, but is you give a "pure" region (the kind of region that is only allowed to go to one part of a split) to the $\lrr$-relation, then the memory satisfation does not have it, and it cannot find a memory segment for this part. In other words, the memory satisfaction will not be able to find a concrete memory segment for segments governed by a linear capability in the register file. Maybe the memory satisfaction should have all of the parts, so it can represent them (but also limit what linear capabilities can be used).}

@@

\[
  \lrv(W) =
  \begin{array}[t]{l}
    \left\{ \npair{\stpair[.]{i}{i}} \middle| i \in \ints \right\}\cup \\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrc(\sigma,\_)},\\\sealed{\sigma,\vsc_C}\endarray\right)} \middle| 
    \begin{array}{l}
    \forall n'<n, W' \pubft W, W_\lrv \npair[n']{\stpair[.]{\retptrd(\sigma,\_)}{\sealed{\sigma,\vsc_D}}} \in \lrv(W_\lrv) \ldotp\\
      \npair[n']{\retptrc(\sigma,\_),\retptrd(\sigma,\_),\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W' \uplus W_\lrv)
    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l}\src{\retptrd(\sigma,\_)},\\\sealed{\sigma,\vsc_D}\endarray\right)} \middle| 
    \begin{array}{l}
    \forall n'<n, W' \pubft W, W_\lrv \npair[n']{\stpair[.]{\retptrc(\sigma,\_)}{\sealed{\sigma,\vsc_C}}} \in \lrv(W_\lrv) \ldotp\\
      \npair[n']{\src{\retptrc(\sigma,\_)},\src{\retptrd(\sigma,\_)},\sealed{\sigma,\vsc_C},\sealed{\sigma,\vsc_D}} \in \lrk(W' \uplus W_\lrv)
    \end{array}
    \right\}\cup \\
    \left\{ \npair{\left(\array{l}\src{\sealed{\sigma,\vsc_S}},\\ \sealed{\sigma,\vsc_T} \endarray\right)} \middle|
    \begin{array}{l}

    \end{array}
    \right\}\cup\\
    \left\{ \npair{\left(\arraycolsep=0pt\array{l} \src{\stkptr{\perm,\baddr,\eaddr,\aaddr}},\\ ((\perm,\linear),\baddr,\eaddr,\aaddr) \endarray \middle| \right)}
    \right\}
  \end{array}
\]
